Evaluating the Supportive Effect of Feature Selection Methods on Machine Learning Models in Monitoring Forest Health Using Hyperspectral Remote Sensing Data

### 2020-04-05 docs/00-manuscripts/ieee/ieee-manuscript.tex
AB-review: wording

\IEEEPARstart{T}{he} use of \ac{ML} algorithms for analyzing remote sensing data has seen a huge increase in the last decade~\cite{lary2016}.
This goes in line with the increased availability of remote sensing imagery, especially since the launch of the first Sentinel satellite in the year 2014.
At the same time, the implementation and usability of learning algorithms has been greatly simplified with many contributions from open-source efforts.
Scientists can nowadays relatively easily process large amounts of (environmental) information using various learning algorithms.
This makes it possible to extend the matrix of possible options in a semi-automated way, possibly stumbling across unexpected findings of process settings that would have never been tested otherwise~\cite{ma2015}.

@@

Machine learning methods in combination with remote sensing data are used in many environmental fields such as vegetation cover analysis or forest carbon storage mapping\cite{mascaro2014, urban2018}.
The ability of predicting to large unknown areas qualifies these tools as a promising toolset for such tasks.
One aspect of this research field is to enhance the understanding of biotic and abiotic triggers, for example by analyzing defoliation at trees\cite{hawrylo2018}.

Other approaches for analyzing forest health include temporal change detection\cite{zhang2016} or describing the current health status of forests on a stand level\cite{townsend2012}.
In such studies, the defoliation of trees serves as a proxy for forest health by describing the impact of biotic and abiotic pest triggers\cite{townsend2012, goodbody2018}.

Vegetation indices have shown the potential to provide valuable information when analyzing forest health\cite{jiang2014, adamczyk2015}.
Most vegetation indices were developed with the aim of being sensitive to changes of specific wavelength regions, serving as a proxy for underlying plant processes. 
However, often enough indices developed for different purposes than the one to be analyzed can help explaining complex relationships.
This emphasizes the need to extract as much information as possible from the available input data to generate promising features which can help understanding the modeled relationship.
A less known index type which can be derived from spectral information is called normalized ratio index (NRI).
In contrast to \ac{VI}, \ac{NRI}s are not based on an expert-based formulas following environmental heuristics but use a data-driven feature engineering approach by combining (arbitrary) combinations of spectral bands.
Especially when working with hyperspectral data, hundreds of \ac{NRI} features can be derived this way.

>>>>

\IEEEPARstart{T}{he} use of \ac{ML} algorithms for analyzing remote sensing data has seen a huge increase in the last decade~\cite{lary2016}.
This goes in line with the increased availability of remote sensing imagery, especially since the launch of the first Sentinel satellite in the year 2014.
At the same time, the implementation and usability of learning algorithms has been greatly simplified with many contributions from the open-source community.
Scientists can nowadays relatively easily process large amounts of (environmental) information using various learning algorithms.
This makes it possible to extend the matrix of possible options in a semi-automated way, possibly stumbling across unexpected findings of process settings that would have never been tested otherwise~\cite{ma2015}.

@@

Machine learning methods in combination with remote sensing data are used in many environmental fields such as vegetation cover analysis or forest carbon storage mapping \cite{mascaro2014, urban2018}.
The ability of predicting to large unknown areas qualifies these tools as a promising toolset for such tasks.
One aspect of this research field is to enhance the understanding of biotic and abiotic triggers, for example by analyzing defoliation at trees \cite{hawrylo2018}.

Other approaches for analyzing forest health include temporal change detection \cite{zhang2016} or describing the current health status of forests on a stand level \cite{townsend2012}.
In such studies, the defoliation of trees serves as a proxy for forest health by describing the impact of biotic and abiotic pest triggers \cite{townsend2012, goodbody2018}.

Vegetation indices have shown the potential to provide valuable information when analyzing forest health \cite{jiang2014, adamczyk2015}.
Most vegetation indices were developed with the aim of being sensitive to changes of specific wavelength regions, serving as a proxy for underlying plant processes. 
However, often enough indices developed for different purposes than the one to be analyzed can help to explain complex relationships.
This emphasizes the need to extract as much information as possible from the available input data to generate promising features which can help to understand the modeled relationship.
A less known index type which can be derived from spectral information is called normalized ratio index (NRI).
In contrast to \ac{VI}, \ac{NRI}s are not based on an expert-based formulas following environmental heuristics but use a data-driven feature engineering approach by combining (arbitrary) combinations of spectral bands.
Especially when working with hyperspectral data, hundreds of \ac{NRI} features can be derived this way.
